Decisions Decisions Decisions: Carrying out Latent Profile Analysis in Accordance With Best Practices Using the tidyLPA R package

### 2020-12-26 paper.rmd
update manuscript

knitr::clean_cache()
knitr::opts_chunk$set(cache.extra = knitr::rand_seed, warning = FALSE)
```

@@

# Specific Software Tools

@@

## tidyLPA

@@

Here, we use a simulated dataset contains data on moral relevance and judgment across the seven domains of the *Morality As Cooperation* scale. More on this scale can be found in Curry et al., (2019).

@@

``` {r, curry-mac-mclust-example}
m1 <- curry_mac %>% 
  select(KinshipR:PossessionR, 
         KinshipJ:PossessionJ) %>% 
  estimate_profiles(1:10) %>% 
  knitr::kable()
```

@@

```{r, get-fit-m1}
get_fit(m1) %>% 
  knitr::kable()
```

``` {r, curry-mac-mplus, eval = FALSE}
curry_mac %>% 
  select(KinshipR:PossessionR, 
         KinshipJ:PossessionJ) %>% 
  estimate_profiles(1:10, package = "mplus")
```

@@

Here is an example of specifying a model with varying variances and covariances
(Model 6)

``` {r, curry-mac-m6, eval = TRUE}
curry_mac %>% 
  select(KinshipR:PossessionR, 
         KinshipJ:PossessionJ) %>% 
  estimate_profiles(3, 
                    variances = "varying",
                    covariances = "varying")
```

````{r, compare-mclust, eval= TRUE}
compare_solutions_mclust <- curry_mac %>% 
  select(KinshipJ:PossessionJ) %>% 
  estimate_profiles(models = c(1, 2, 3, 6),
                    n_profiles = 1:9,
                    package = "mclust") %>% 
  knitr::kable()
```

```{r, eval = FALSE, echo = FALSE}
write_rds(compare_solutions_mclust, "compare_solutions_mclust.rds")
```

```{r, echo = FALSE}
compare_solutions_mclust <- read_rds("compare_solutions_mclust.rds")
compare_solutions_mclust
```

```{r, compare-mplus, eval = FALSE}
compare_solutions_mplus <- curry_mac %>% 
  select(KinshipJ:PossessionJ) %>% 
  estimate_profiles(models = c(1, 2, 3, 4, 5, 6),
                    n_profiles = 1:9,
                    package = "mplus") %>% 
  knitr::kable()
```

```{r, echo = FALSE, eval = FALSE}
write_rds(compare_solutions_mplus, "compare_solutions_mplus.rds")
```

```{r, echo = FALSE}
compare_solutions_mplus <- read_rds("compare_solutions_mplus.rds")
compare_solutions_mplus
```

```{r, compare-mplus-starts, eval = TRUE}
compare_solutions_mplus_starts <- curry_mac %>% 
  select(KinshipJ:PossessionJ) %>% 
  estimate_profiles(models = c(1, 2, 3, 4, 5, 6),
                    n_profiles = 1:9,
                    package = "mplus",
                    ANALYSIS = "starts = 100, 20;") %>% 
  knitr::kable()
```

```{r, echo = FALSE, eval = FALSE}
write_rds(compare_solutions_mplus_starts, "compare_solutions_mplus_starts.rds")
```

```{r, echo = FALSE}
compare_solutions_mplus <- read_rds("compare_solutions_mplus_starts.rds")
compare_solutions_mplus
```

The results of this analysis suggests that the Model 6, two or seven class models are best.

@@

``` {r, eval = FALSE}
get_data()
```

@@

``` {r, eval = FALSE}
get_data(m) %>% 
  tidyr::gather(Class_prob, Probability, contains("CPROB"))
```

@@

## How the Data are Centering or Scaled

The data can be transformed by centering or scaling. Typically, these are done
after the profiles are created, so that differences between profiles can be more
easily explored. They can also be done prior to the analysis, which can be
helpful for obtaining solutions when the variables are on very different
scales.

## How to Choose the Number of Profiles/Classes

## How to Choose Options for the Clustering Procedure or to Select the Model Parameterization

## More General Recommendations

This section highlights three general recommendations. First, scholars taking a
person-oriented approach should emphasize reproducibility in carrying out
analyses. This is in part due to the exploratory and interpretative nature of
person-oriented approaches. To this end, presenting multiple models, as in
Pastor et al. (2007), should be encouraged, rather than presenting one solution.
In addition, having multiple analysts review the solutions found is encouraged.
As part of this recommendation, we suggest that researchers consider how their
analyses can be reproduced by other analysts outside of the research team:
Sharing code and data is an important part of this work. Also related,
researchers should consider how profiles are replicated across samples.

>>>>

knitr::clean_cache()
knitr::opts_chunk$set(cache.extra = knitr::rand_seed, warning = FALSE, cache = TRUE)
```

@@

# Best Practices for Latent Profile Analysis

# tidyLPA

@@

## The tidyLPA R package

@@

Here, we use a simulated dataset contains data on broad interest, enjoyment, and self-efficacy from the PISA assessment.

First, let's explore the data graphically using the {ggplot2} package:

```{r}
pisaUSA15 %>%
  select(broad_interest, enjoyment, self_efficacy) %>% 
  tidyr::gather(key, val) %>% 
  ggplot(aes(x = val, group = key, fill = key)) + 
  geom_density() + 
  facet_wrap(~key) + 
  theme_bw()
```

Here, we use the {psych} package to explore the distributional properties of the variables:

```{r}
pisaUSA15 %>%
  select(broad_interest, enjoyment, self_efficacy) %>% 
  psych::describe()
```

@@

``` {r, curry-mac-mclust-example}
pisaUSA15 %>%
  select(broad_interest, enjoyment, self_efficacy) %>%
  single_imputation() %>%
  estimate_profiles(3)
```

``` {r, curry-mac-mplus, eval = FALSE}
pisaUSA15 %>%
  select(broad_interest, enjoyment, self_efficacy) %>%
  single_imputation() %>%
  estimate_profiles(3, package = "mplus")
```

### Fit

@@

```{r, get-fit-m1}
pisaUSA15 %>%
  select(broad_interest, enjoyment, self_efficacy) %>%
  single_imputation() %>%
  estimate_profiles(3) %>% 
  get_fit(m1) %>% 
  knitr::kable()
```

````{r, compare-mclust, eval= TRUE}
compare_solutions_results <- pisaUSA15 %>%
  select(broad_interest, enjoyment, self_efficacy) %>%
  single_imputation() %>%
  estimate_profiles(models = c(1, 2, 3, 6),
                    n_profiles = 1:9)

compare_solutions_results

compare_solutions(compare_solutions_results)
```

@@

@@

``` {r, get-data-for-solution, eval = FALSE}
get_data(compare_solutions_mclust[[32]])
```

@@

``` {r, process-data, eval = FALSE}
get_data(compare_solutions_mclust[[32]]) %>% 
  tidyr::gather(Class_prob, Probability, contains("CPROB"))
```

@@

# Future Directions and Extensions

First, scholars taking a
person-oriented approach should emphasize reproducibility in carrying out
analyses. This is in part due to the exploratory and interpretative nature of
person-oriented approaches. To this end, presenting multiple models, as in
Pastor et al. (2007), should be encouraged, rather than presenting one solution.
In addition, having multiple analysts review the solutions found is encouraged.
As part of this recommendation, we suggest that researchers consider how their
analyses can be reproduced by other analysts outside of the research team:
Sharing code and data is an important part of this work. Also related,
researchers should consider how profiles are replicated across samples.

### 2020-12-26 paper.tex
update manuscript

\shorttitle{tidyLPA}
\affiliation{
\vspace{0.5cm}
\textsuperscript{1} University of Tennessee, Knoxville\\\textsuperscript{2} Utrecht University\\\textsuperscript{3} Michigan State University\\\textsuperscript{4} University of Oregon\\\textsuperscript{5} }
\keywords{Latent Profile Analysis, mixture models, finite mixture models, tutorial, R, MPlus, mclust\newline\indent Word count: }
\usepackage{csquotes}
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

@@

@@

@@

In this tutorial, we aim to describe one of the most commonly-used--and relevant
to psychologists--application of the general mixture model, to cases for which
all of the variables for which (relatively) homogeneous groups are identified
from among a (relatively) heterogeneous sample are continuos, \emph{latent profile
analysis} (LPA). We note that scholars using the approach, especially in
developmental and educational psychology, use cluster analytic methods. Such an
approach has some similarities with LPA (CITE paper showing how k-means is
similar to the simplest model specification of LPA?), though LPA also has a
number of benefits (Linnenbrink-Garcia \& Wormington, 2017), and we we focus on
LPA in this paper.

@@

The goal of LPA is estimate the parameters for a number of distributions
(typically multivariate) from a single dataset. Thus, such an approach is
model-based, and some descriptions in the literature refer to it as model-based
clustering (Hennig, Meila, Murtagh, \& Rocci, 2015; Scrucca, Fop, Murphy, \&
Raftery, 2017). Thus, one distinction between LPA and other, similar cluster
analytic approaches is that LPA is model-based; instead of using algorithms to
group together cases, LPA seeks to estimate parameters - in terms of variances
and covariances and how they are the same or different across profiles - that
best characterize the different distributions. Then, this approach seeks to
assign to each observation a probability that the observation is a sample from
the population associated with each profile (or mixture component).

@@

We wish to note that challenge facing the analyst using LPA is that these
parameters and the distinct model parameterizations that can be estimated is the
different terminology used. As one example, Scrucca et al. (2017) refer to these
parameterizations not in terms of whether and how parameters are estimated, but
rather in terms of the geometric properties of the distributions that result
from particular parameterizations. Muthen and Muthen (1997-2017) and others
(Pastor et al., 2007) commonly refer to local independence to mean that the
covariances are fixed to zero (also described as the specification of the
covariance matrix as \enquote{diagonal,} because only the diagonal components, or the
variances, are estimated).

@@

\hypertarget{other-tools}{%
\subsection{Other Tools}\label{other-tools}}

@@

You can install tidyLPA from CRAN with:

You can also install the development version of tidyLPA from GitHub with:

\begin{verbatim}
## Warning: package 'tidyLPA' was built under R version 3.6.2
\end{verbatim}

@@

Here, we use a simulated dataset, based on Curry et al., 2019, contains data on moral relevance and judgment across the seven domains of the \emph{Morality As Cooperation} scale.

@@

We can see a number of statistics for each of the models that were estimated, including the
AIC (Aikake information criterion; based on -2 log-likelihood, and penalized by number of parameters) and BIC (BIC: Bayesian information criterion; based on -2 log-likelihood, and penalized by number of parameters adjusted by sample size). Both are \emph{penalized} likelihood statistics; the log-likelihood will always decrease with the addition of additional
paremeters estimated by the model, whereas the AIC and BIC will account for the number of parameters; lower values of
either indicate better fit.

@@

\begin{verbatim}
## # A tibble: 10 x 18
##    Model Classes  LogLik    AIC    AWE    BIC   CAIC    CLC    KIC  SABIC
##    <dbl>   <dbl>   <dbl>  <dbl>  <dbl>  <dbl>  <dbl>  <dbl>  <dbl>  <dbl>
##  1     1       1 -81245. 1.63e5 1.63e5 1.63e5 1.63e5 1.62e5 1.63e5 1.63e5
##  2     1       2 -79727. 1.60e5 1.60e5 1.60e5 1.60e5 1.59e5 1.60e5 1.60e5
##  3     1       3 -79239. 1.59e5 1.59e5 1.59e5 1.59e5 1.58e5 1.59e5 1.59e5
##  4     1       4 -79091. 1.58e5 1.59e5 1.59e5 1.59e5 1.58e5 1.58e5 1.58e5
##  5     1       5 -79029. 1.58e5 1.60e5 1.59e5 1.59e5 1.58e5 1.58e5 1.58e5
##  6     1       6 -78971. 1.58e5 1.60e5 1.59e5 1.59e5 1.58e5 1.58e5 1.58e5
##  7     1       7 -78930. 1.58e5 1.60e5 1.59e5 1.59e5 1.58e5 1.58e5 1.58e5
##  8     1       8 -78852. 1.58e5 1.60e5 1.59e5 1.59e5 1.58e5 1.58e5 1.58e5
##  9     1       9 -78822. 1.58e5 1.60e5 1.59e5 1.59e5 1.58e5 1.58e5 1.58e5
## 10     1      10 -78751. 1.58e5 1.60e5 1.59e5 1.59e5 1.58e5 1.58e5 1.58e5
## # ... with 8 more variables: ICL <dbl>, Entropy <dbl>, prob_min <dbl>,
## #   prob_max <dbl>, n_min <dbl>, n_max <dbl>, BLRT_val <dbl>, BLRT_p <dbl>
\end{verbatim}

@@

Here is an example of specifying a model with varying variances and covariances
(Model 6; not run here):

@@

\begin{verbatim}
## Warning: 
## One or more analyses resulted in warnings! Examine these analyses carefully: model_1_class_6, model_1_class_7, model_1_class_8, model_1_class_9, model_2_class_5, model_2_class_6, model_2_class_7, model_2_class_8, model_2_class_9, model_3_class_1, model_3_class_2, model_3_class_3, model_3_class_4, model_3_class_5, model_3_class_6, model_3_class_7, model_3_class_8, model_3_class_9, model_4_class_1, model_4_class_2, model_4_class_3, model_4_class_4, model_4_class_5, model_4_class_6, model_4_class_7, model_4_class_8, model_4_class_9, model_5_class_1, model_5_class_2, model_5_class_3, model_5_class_4, model_5_class_5, model_5_class_6, model_5_class_7, model_5_class_8, model_5_class_9, model_6_class_3, model_6_class_4, model_6_class_5, model_6_class_6, model_6_class_7, model_6_class_8, model_6_class_9
\end{verbatim}

\begin{verbatim}
## Warning: 
## One or more analyses resulted in warnings! Examine these analyses carefully: model_1_class_7, model_1_class_8, model_1_class_9, model_2_class_6, model_2_class_7, model_2_class_8, model_2_class_9, model_3_class_1, model_3_class_2, model_3_class_3, model_3_class_4, model_3_class_5, model_3_class_6, model_3_class_7, model_3_class_8, model_3_class_9, model_4_class_1, model_4_class_2, model_4_class_3, model_4_class_4, model_4_class_5, model_4_class_6, model_4_class_7, model_4_class_8, model_4_class_9, model_5_class_1, model_5_class_2, model_5_class_3, model_5_class_4, model_5_class_5, model_5_class_6, model_5_class_7, model_5_class_8, model_5_class_9, model_6_class_3, model_6_class_4, model_6_class_5, model_6_class_6, model_6_class_7, model_6_class_8, model_6_class_9
\end{verbatim}

The results of this analysis suggests that the Model 6, two or seven class models are best.

@@

\hypertarget{htmlwidget-31a3e9100620ea87273d}{}

>>>>

\shorttitle{LPA Best Practices}
\affiliation{
\vspace{0.5cm}
\textsuperscript{1} University of Tennessee, Knoxville\\\textsuperscript{2} Utrecht University\\\textsuperscript{3} Michigan State University\\\textsuperscript{4} University of Oregon\\\textsuperscript{5} }
\keywords{Latent Profile Analysis, mixture models, finite mixture models, tutorial, R, MPlus, mclust\newline\indent Word count: }
\usepackage{csquotes}
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

\begin{verbatim}
## Warning: package 'ggplot2' was built under R version 3.6.2
\end{verbatim}

@@

\begin{verbatim}
## Warning: package 'tidyr' was built under R version 3.6.2
\end{verbatim}

\begin{verbatim}
## Warning: package 'readr' was built under R version 3.6.2
\end{verbatim}

@@

\begin{verbatim}
## Warning: package 'simstudy' was built under R version 3.6.2
\end{verbatim}

@@

In this tutorial, we aim to describe one of the most commonly-used--and relevant
to psychologists---application of the general mixture model, to cases for which
all of the variables for which (relatively) homogeneous groups are identified
from among a (relatively) heterogeneous sample are continuos, \emph{latent profile
analysis} (LPA). We note that scholars using the approach, especially in
developmental and educational psychology, use cluster analytic methods. Such an
approach has some similarities with LPA (CITE paper showing how k-means is
similar to the simplest model specification of LPA?), though LPA also has a
number of benefits (Linnenbrink-Garcia \& Wormington, 2017), and we we focus on
LPA in this paper.

@@

The goal of LPA is estimate the parameters for a number of distributions
(typically multivariate) from a single data set. Thus, such an approach is
model-based, and some descriptions in the literature refer to it as model-based
clustering (Hennig, Meila, Murtagh, \& Rocci, 2015; Scrucca, Fop, Murphy, \&
Raftery, 2017). Thus, one distinction between LPA and other, similar cluster
analytic approaches is that LPA is model-based; instead of using algorithms to
group together cases, LPA seeks to estimate parameters - in terms of variances
and covariances and how they are the same or different across profiles - that
best characterize the different distributions. Then, this approach seeks to
assign to each observation a probability that the observation is a sample from
the population associated with each profile (or mixture component).

@@

We note that challenge facing the analyst using LPA is that these
parameters and the distinct model parameterizations that can be estimated is the
different terminology used. As one example, Scrucca et al. (2017) refer to these
parameterizations not in terms of whether and how parameters are estimated, but
rather in terms of the geometric properties of the distributions that result
from particular parameterizations. Muthen and Muthen (1997-2017) and others
(Pastor et al., 2007) commonly refer to local independence to mean that the
covariances are fixed to zero (also described as the specification of the
covariance matrix as \enquote{diagonal,} because only the diagonal components, or the
variances, are estimated).

@@

\hypertarget{tools-other-than-tidylpa}{%
\subsection{Tools other than tidyLPA}\label{tools-other-than-tidylpa}}

@@

You can install tidyLPA from the Comprehensive R Archive Network, or CRAN, with:

This is how we recommend most users install tidyLPA.

You can also install the development version of tidyLPA, which may have new features that are not yet availalble on CRAN (because the version on CRAN is periodically updated) from GitHub with:

@@

Here, we use a simulated dataset contains data on moral relevance and judgment across the seven domains of the \emph{Morality As Cooperation} scale. More on this scale can be found in Curry et al., (2019).

Add one or two sentences here on the dataset?

@@

Note that here and throughout this paper we use the function \texttt{knitr::kable()} to
format the output in an RMarkdown document, like the one we are using; this is
not necessary to use unless you also wish to format the tidyLPA output in an
RMarkdown document.

We can see a number of statistics for each of the models that were estimated, including the
AIC (Aikake information criterion; based on -2 * the log-likelihood, and penalized by number of parameters) and BIC (BIC: Bayesian information criterion; based on -2 log-likelihood, and penalized by number of parameters adjusted by sample size). Both are \emph{penalized} likelihood statistics; the log-likelihood will always decrease with the addition of additional
paremeters estimated by the model, whereas the AIC and BIC will account for the number of parameters; lower values of
either indicate better fit.

@@

\begin{tabular}{r|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r}
\hline
Model & Classes & LogLik & AIC & AWE & BIC & CAIC & CLC & KIC & SABIC & ICL & Entropy & prob\_min & prob\_max & n\_min & n\_max & BLRT\_val & BLRT\_p\\
\hline
1 & 1 & -81245.00 & 162546.0 & 162977.4 & 162692.7 & 162720.7 & 162492.0 & 162577.0 & 162603.7 & -162692.7 & 1.0000000 & 1.0000000 & 1.0000000 & 1.0000000 & 1.0000000 & NA & NA\\
\hline
1 & 2 & -79727.50 & 159541.0 & 160204.8 & 159766.3 & 159809.3 & 159456.7 & 159587.0 & 159629.7 & -159925.3 & 0.8369494 & 0.9296991 & 0.9637189 & 0.3441092 & 0.6558908 & 3035.00346 & 0.009901\\
\hline
1 & 3 & -79239.27 & 158594.5 & 159490.6 & 158898.4 & 158956.4 & 158480.2 & 158655.5 & 158714.1 & -159175.7 & 0.8188766 & 0.9053581 & 0.9222054 & 0.1465517 & 0.5272989 & 976.44661 & 0.009901\\
\hline
1 & 4 & -79090.59 & 158327.2 & 159455.5 & 158709.6 & 158782.6 & 158182.7 & 158403.2 & 158477.7 & -159150.2 & 0.7763719 & 0.8393595 & 0.9127306 & 0.0732759 & 0.4655172 & 297.35974 & 0.009901\\
\hline
1 & 5 & -79029.50 & 158235.0 & 159595.6 & 158696.0 & 158784.0 & 158060.4 & 158326.0 & 158416.4 & -159398.5 & 0.7012112 & 0.6979575 & 0.8987374 & 0.0675287 & 0.2406609 & 122.19715 & 0.009901\\
\hline
1 & 6 & -78971.30 & 158148.6 & 159741.3 & 158688.2 & 158791.2 & 157944.0 & 158254.6 & 158361.0 & -159456.7 & 0.6954594 & 0.6929238 & 0.9230731 & 0.0603448 & 0.3060345 & 116.39215 & 0.009901\\
\hline
1 & 7 & -78930.08 & 158096.2 & 159921.0 & 158714.3 & 158832.3 & 157861.5 & 158217.2 & 158339.5 & -159550.6 & 0.6933730 & 0.5964096 & 0.9236077 & 0.0610632 & 0.2550287 & 82.44963 & 0.009901\\
\hline
1 & 8 & -78851.80 & 157969.6 & 160026.5 & 158666.3 & 158799.3 & 157705.1 & 158105.6 & 158243.8 & -159391.4 & 0.7477064 & 0.6432919 & 0.9219048 & 0.0423851 & 0.2902299 & 156.55019 & 0.009901\\
\hline
1 & 9 & -78821.74 & 157939.5 & 160228.6 & 158714.8 & 158862.8 & 157645.0 & 158090.5 & 158244.6 & -159455.8 & 0.7515427 & 0.6071032 & 0.9456474 & 0.0402299 & 0.2938218 & 60.12578 & 0.009901\\
\hline
1 & 10 & -78751.27 & 157828.5 & 160349.8 & 158682.4 & 158845.4 & 157504.1 & 157994.5 & 158164.6 & -159420.9 & 0.7625067 & 0.6463008 & 0.9396876 & 0.0337644 & 0.2909483 & 140.92881 & 0.009901\\
\hline
\end{tabular}

@@

Here is an example of specifying a model with varying variances and covariances
(Model 6)

\begin{verbatim}
## tidyLPA analysis using mclust: 
## 
##  Model Classes AIC       BIC       Entropy prob_min prob_max n_min n_max BLRT_p
##  6     3       156872.22 158752.84 0.67    0.82     0.87     0.23  0.41  0.01
\end{verbatim}

@@

\begin{verbatim}
## tidyLPA analysis using mclust: 
## 
##  Model Classes AIC       BIC       Entropy prob_min prob_max n_min n_max BLRT_p
##  1     1       139226.33 139352.05 1.00    1.00     1.00     1.00  1.00        
##  1     2       136511.15 136704.97 0.83    0.92     0.97     0.34  0.66  0.01  
##  1     3       135651.76 135913.69 0.81    0.90     0.92     0.14  0.53  0.01  
##  1     4       135391.00 135721.03 0.77    0.83     0.91     0.07  0.47  0.01  
##  1     5       135326.12 135724.24 0.72    0.57     0.91     0.07  0.39  0.01  
##  1     6       135281.64 135747.86 0.68    0.56     0.92     0.07  0.28  0.01  
##  1     7       135218.07 135752.39 0.67    0.59     0.91     0.07  0.29  0.01  
##  1     8       135135.62 135738.04 0.70    0.59     0.92     0.05  0.31  0.01  
##  1     9       135098.58 135769.10 0.70    0.57     0.93     0.05  0.30  0.01  
##  2     1       139226.33 139352.05 1.00    1.00     1.00     1.00  1.00        
##  2     2       136245.76 136502.44 0.81    0.92     0.96     0.39  0.61  0.01  
##  2     3       135337.03 135724.68 0.80    0.91     0.91     0.25  0.49  0.01  
##  2     4       135103.11 135621.72 0.75    0.82     0.92     0.17  0.37  0.01  
##  2     5       134840.49 135490.07 0.75    0.76     0.89     0.13  0.31  0.01  
##  2     6       134688.81 135469.35 0.75    0.71     0.89     0.06  0.29  0.01  
##  2     7       134579.47 135490.97 0.75    0.64     0.90     0.06  0.23  0.01  
##  2     8       134482.30 135524.76 0.75    0.71     0.90     0.06  0.18  0.01  
##  2     9       134434.76 135608.19 0.75    0.65     0.91     0.06  0.17  0.01  
##  3     1       134912.97 135384.44 1.00    1.00     1.00     1.00  1.00        
##  3     2       134836.15 135375.72 0.69    0.78     0.96     0.22  0.78  0.01  
##  3     3       134862.13 135469.80 0.41    0.16     0.88     0.07  0.69  0.76  
##  3     4       134728.94 135404.71 0.50    0.31     0.83     0.10  0.63  0.01  
##  3     5       134615.77 135359.63 0.58    0.43     0.79     0.07  0.56  0.01  
##  3     6       134696.35 135508.32 0.52    0.43     0.81     0.06  0.39  0.71  
##  3     7       134589.15 135469.21 0.54    0.36     0.84     0.06  0.37  0.01  
##  3     8       134604.12 135552.29 0.54    0.40     0.84     0.04  0.33  0.77  
##  3     9       134568.05 135584.32 0.56    0.31     0.83     0.03  0.34  0.01  
##  6     1       134912.97 135384.44 1.00    1.00     1.00     1.00  1.00        
##  6     2       134223.62 135171.78 0.62    0.87     0.90     0.48  0.52  0.01  
##  6     3       134151.67 135576.55 0.68    0.80     0.88     0.18  0.47  0.01  
##  6     4       134089.83 135991.41 0.68    0.77     0.87     0.17  0.36  0.01  
##  6     5       134092.59 136470.87 0.71    0.77     0.89     0.06  0.33  0.34  
##  6     6       134088.85 136943.83 0.72    0.75     0.90     0.06  0.29  0.43  
##  6     7       134021.25 137352.94 0.74    0.77     0.88     0.09  0.20  0.01  
##  6     8       134038.51 137846.90 0.77    0.79     0.98     0.03  0.19  0.58  
##  6     9       134067.02 138352.11 0.78    0.77     0.96     0.04  0.18  0.78
\end{verbatim}

\begin{verbatim}
## Compare tidyLPA solutions:
## 
##  Model Classes BIC       
##  1     1       139352.049
##  1     2       136704.970
##  1     3       135913.687
##  1     4       135721.026
##  1     5       135724.243
##  1     6       135747.862
##  1     7       135752.395
##  1     8       135738.044
##  1     9       135769.104
##  2     1       139352.049
##  2     2       136502.441
##  2     3       135724.680
##  2     4       135621.724
##  2     5       135490.065
##  2     6       135469.349
##  2     7       135490.971
##  2     8       135524.760
##  2     9       135608.188
##  3     1       135384.436
##  3     2       135375.718
##  3     3       135469.796
##  3     4       135404.708
##  3     5       135359.634
##  3     6       135508.318
##  3     7       135469.214
##  3     8       135552.290
##  3     9       135584.321
##  6     1       135384.436
##  6     2       135171.784
##  6     3       135576.546
##  6     4       135991.409
##  6     5       136470.871
##  6     6       136943.826
##  6     7       137352.936
##  6     8       137846.896
##  6     9       138352.109
## 
## Best model according to BIC is Model 6 with 2 classes.
## 
## An analytic hierarchy process, based on the fit indices AIC, AWE, BIC, CLC, and KIC (Akogul & Erisoglu, 2017), suggests the best solution is Model 6 with 2 classes.
\end{verbatim}

\includegraphics{paper_files/figure-latex/plot-one-solution-1.pdf}

@@

\hypertarget{htmlwidget-675d126ab2afaf44720a}{}
